### 2017-12-08 submission/manuscript.Rmd
add completed rough Results workflow -- need stats still

***Chimeric Sequences are HiFi Taq Dependent:***
After chimera removal using VSEARCH and removal of sequences that did not classify as bacteria we assessed the percentage of sequences that were still chimeric within our mock community. From this we observed that Platinum HiFi conssitently had the highest percentage of chimeric reads regardless of amplification cycle number and sub-sampling depth [Figure 4]. These results mirror the observations of increased number of OTUs and the increased median average per base error [Figure 2-4].

>>>>

***Chimeric Sequences Corelate with OTUs and are HiFi Taq Dependent:***
After chimera removal using VSEARCH and removal of sequences that did not classify as bacteria we assessed the percentage of sequences that were still chimeric within our mock community. From this we observed that Platinum HiFi conssitently had the highest percentage of chimeric reads regardless of amplification cycle number and sub-sampling depth [Figure 4]. For all Taqs a positive correlation was observed between chimeric sequences and number of OTUs and this correlation was strongest for Platinum and Phusion HiFi Taq [Figure 5]. In general the correlations between the number of OTUs and chimeric sequences became stronger as sub-sampling depth increased [Figure 5].

### 2017-12-08 submission/manuscript.tex
add completed rough Results workflow -- need stats still

\textbf{\emph{Sequence Processing:}} The mothur software program was
utilized for all sequence processing steps (Schloss et al., 2009). The
protocol followed was similar to what has been previously publsihed
(Kozich et al., 2013) (\url{https://www.mothur.org/wiki/MiSeq_SOP}). Two
major differences from the stated protocol were the use VSEARCH instead
of UCHIME for chimera detection and the use of the OptiClust algorithmn
instead of average neighbor for OTU generation (Edgar et al., 2011;
Rognes et al., 2016; Westcott \& Schloss, 2017). Sequence error was
determined using the seq.error command on mock samples after chimera
removal and classification to the RDP to remove non-bacterial sequences
(Schloss et al., 2009; Cole et al., 2013; Rognes et al., 2016).

@@

\textbf{\emph{Insert Sub title here}}

>>>>

\textbf{\emph{Sequence Processing:}} The mothur software program was
utilized for all sequence processing steps (Schloss et al., 2009). The
protocol followed was similar to what has been previously publsihed
(Kozich et al., 2013) (\url{https://www.mothur.org/wiki/MiSeq_SOP}). Two
major differences from the stated protocol were the use VSEARCH instead
of UCHIME for chimera detection and the use of the OptiClust algorithmn
instead of average neighbor for Operational Taxonomic Unit (OTU)
generation (Edgar et al., 2011; Rognes et al., 2016; Westcott \&
Schloss, 2017). Sequence error was determined using the seq.error
command on mock samples after chimera removal and classification to the
RDP to remove non-bacterial sequences (Schloss et al., 2009; Cole et
al., 2013; Rognes et al., 2016).

@@

\textbf{\emph{The Number of OTUs is Dependent on HiFi Taq Used:}} After
normalization by individual, for each cycle number, we observed that for
fecal samples the number of OTUs identified was dependent upon the HiFi
Taq used and this difference increased as the depth of sub-sampling
increased {[}Figure 1{]}. Lower cycle numbers (15-25) resulted in less
differences between Taq while cycle numbers of 30 and 35 had larger
clearer defined differences {[}Figure 1{]}. Generally, the lowest number
of OTUs identified was from Accuprime\textsuperscript{TM} while the
highest was from Platinum {[}Figure 1{]}. This Taq dependent difference
in the number of OTUs was also observed in the mock community samples
with the same Taq polymerases being high (Platinum) and low (Accuprime)
respectively {[}Figure 2{]}.

\textbf{\emph{Per Base Error Rate is Dependent on both Taq and Cycle
Number Used:}} The median average per base error was highest for the
Kappa HiFI Taq {[}FIgure 3A{]}. Sub-sampling depth seems to have little
effect on this rate with both 5000 and 10000 sub-sampled sequences
showing similar results {[}Figure 3B \& C{]}. Generally, there were
small differences between the various HiFi Taq at lower cycle number but
larger differences at higher cycle number {[}Figure 3B \& C{]}. Platinum
HiFi Taq consistently had the highes median average per base error rate
while Phusion and Accuprime had the lowest {[}Figure 3B \& C{]}. These
differences though were realtively small between the different HiFi Taq
{[}Figure 3{]}. The total seqeunces with at least one error matched the
median average per base error except for the Accuprime HiFi Taq
{[}Figure S1{]}. Although it had the lowest per base error rate it had
either the largest or second largest number of sequences with at least
one error regardless of cycle number of sub-sampling depth {[}Figure
S1{]}. Investigation of whether there were Taq dependent effects on base
subsitution found that there was no clear bias and this was indpendent
of sub sampling depth {[}Figure S2-S4{]}. Further, the variation in
subsitution error seems to reduce as the sequencing depth increases
{[}Figure S2-S4{]}.

\textbf{\emph{Chimeric Sequences Corelate with OTUs and are HiFi Taq
Dependent:}} After chimera removal using VSEARCH and removal of
sequences that did not classify as bacteria we assessed the percentage
of sequences that were still chimeric within our mock community. From
this we observed that Platinum HiFi conssitently had the highest
percentage of chimeric reads regardless of amplification cycle number
and sub-sampling depth {[}Figure 4{]}. For all Taqs a positive
correlation was observed between chimeric sequences and number of OTUs
and this correlation was strongest for Platinum and Phusion HiFi Taq
{[}Figure 5{]}. In general the correlations between the number of OTUs
and chimeric sequences became stronger as sub-sampling depth increased
{[}Figure 5{]}.
